Fast Neural Machine Translation Implementation

### 2018-05-24 wnmt.2018/wnmt.tex
bah

As neural machine translation (NMT) models have become the new state-of-the-art, the challenge is to make their deployment efficient and economical. This is the challenge that this shared task is shining a spotlight on.

@@

We describe the main enhancements to Amun since the original 2016 publication.

@@

\subsection{Softmax and Beam Search Fusion}

@@

The output layer of most deep learning models consist of the following steps
\begin{enumerate}
   \item \vspace{-2 mm} multiplication of the weight matrix with the input vector $p = w x$
   \item \vspace{-2 mm} addition of a bias term to the resulting scores $p = p + b$
   \item \vspace{-2 mm} applying the activation function, most commonly softmax $ p_i = \exp(p_i) / \sum \exp(p_i) $
   \item \vspace{-2 mm} a beam search for the best (or n-best) output classes $\argmax_i p_i$
\end{enumerate}

@@

We focus on the last three steps; their outline is shown in Algorithm~\ref{algo:original-softmax-beamsearch}. For brevity, we show the algorithm for 1-best, a beam search of the n-bests is a simple extension of this.

@@

\end{algorithmic}
\caption{Original softmax and beam Search Algorithm}
\label{algo:original-softmax-beamsearch}
\end{algorithm}

@@

\caption{Fused softmax and beam search}
\label{algo:Fused Kernel}
\end{algorithm}

>>>>

As neural machine translation (NMT) models have become the new state-of-the-art, the challenge is to make their deployment efficient and economical. This is the challenge that this shared task~\citep{birch2018wnmt} is shining a spotlight on.

@@

We describe the main enhancements to Amun since the original 2016 publication that has improved translation speed.

@@

\subsection{Softmax and K-Best Fusion}

@@

The output layer of most deep learning models consist of the following steps
\begin{enumerate}
   \item \vspace{-2 mm} multiplication of the weight matrix with the input vector $p = w x$
   \item \vspace{-2 mm} addition of a bias term to the resulting scores $p = p + b$
   \item \vspace{-2 mm} applying the activation function, most commonly softmax $ p_i = \exp(p_i) / \sum \exp(p_i) $
   \item \vspace{-2 mm} a search for the best (or k-best) output classes $\argmax_i p_i$
\end{enumerate}

@@

We focus on the last three steps; their outline is shown in Algorithm~\ref{algo:original-softmax-beamsearch}. For brevity, we show the algorithm for 1-best, a k-best search is a simple extension of this.

@@

\end{algorithmic}
\caption{Original softmax and k-best algorithm}
\label{algo:original-softmax-beamsearch}
\end{algorithm}

@@

\caption{Fused softmax and k-best}
\label{algo:Fused Kernel}
\end{algorithm}
